Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

\textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing. The sizing process involve a set of 18 equations, related to electrical engineering area, which are detailed in <GoogleDrive here>. The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system}

\begin{figure}[h]
\fbox{\includegraphics[width=0.8\textwidth]{flowchart2}}
\centering
\caption{High level description of stand-alone PV system sizing process.}
\label{fig:flow} 
\end{figure}

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the inputs need to size a PV system. There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Related to the equipment list, the designer can use few equipment or a vast one. It is possible, as well, do not adopt commercial equipment list. However, the result is a PV sizing of specific power/current/ or voltage values, and usually just close of real equipment that can be found in the market. That possibility has the drawback of possible incompatibility among equipment when the real one are bought and deployed.}

\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items. Those represent different shades of gray of the  rectangle boxes. The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}. The arrows, in the right side, it shows a point where some specific item is validated. The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux. At the end of the flow, all the items are defined and the sizing is finished.}

\textcolor{blue}{All the 18 equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

@@

 \begin{algorithm}[h]
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
 \STATE Initialize variables \\
 \STATE Declare the maximum possible cost $MaxCost$ \\
 \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
 \FOR {$HintCost=MinCost$ to $MaxCost$} 
 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost \\
	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
 \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$). The directive \textit{assume} (lines $8$, $13$, $14$, and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines. Line $5$ is specific to PV panels. Line $13$ is for the battery bank. Line $14$ is the charge controller voltage check. Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$). This cost is the equivalent to Eq.~\eqref{eq:LCC}.

@@

In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.

%---------------------------------------------------------------------------
\subsection{Threats to validity} 
%---------------------------------------------------------------------------
We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate. Second, improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one. 
%------------------------------------
\section{Conclusions} 
%------------------------------------
Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by the commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market. It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. For future work, we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.

\textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the phase 3 of our synthesis technique, in order to speed up the time to response. Using binary search or even solver that is specific to perform optimization with model checking as $\nu Z$.}

>>>>

\textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing. The sizing process involve a set of eighteen equations, related to electrical engineering area, which are detailed online\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing }}. The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system.}

\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
\centering
\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
\label{fig:flow} 
\end{figure}

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the \textbf{inputs} need to size a PV system. There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Related to the equipment list, the designer can use few equipment or a vast one. It is possible, as well, do not adopt commercial equipment list. However, the result is a PV sizing of specific power/current/ or voltage values, and usually just close of real equipment that can be found in the market. That possibility has the drawback of possible incompatibility among equipment when the real one are bought and deployed.}

\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv} in Fig.~\ref{fig:flow}. Those represent different shades of gray of the  rectangle boxes. The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of the flowchart. The arrows, in the right side, it shows a point where some specific item is validated. The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux. The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from outlet; moreover, the inverter specified power must be lower than the charge controller power in order to avoid it to burn by overcharge. At the end of the flowchart, all the items are defined and the PV sizing is finished.}

\textcolor{blue}{All the equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

\textcolor{blue}{Our mathematical model uses floating point arithmetic. It is just an approximation of the real numbers. However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted~\cite{DBLP:journals/corr/abs-2004-12699}.}

@@

 \begin{algorithm}[h]
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
 \STATE Initialize variables \\
 \STATE Declare the maximum possible cost $MaxCost$ \\
 \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
 \FOR {$HintCost=MinCost$ to $MaxCost$} 
 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
 	\STATE Calculate steps i and ii of Fig.~\ref{fig:flow} \\
	\STATE Define PV panels arrangement: step iii of Fig.~\ref{fig:flow} \\
	\STATE Calculate  step iv of Fig.~\ref{fig:flow} \\
	\STATE Enforce electrical compatibility in step v of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
	\STATE Calculate steps vi to viii of Fig.~\ref{fig:flow} \\
	\STATE Define battery arrangement according step ix of Fig.~\ref{fig:flow} \\
	\STATE Enforce electrical compatibility in step x of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
	\STATE Correct variables to ambient temperature: step xi of Fig.~\ref{fig:flow} \\
	\STATE Enforce electrical compatibility in step xii of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
	\STATE Define number of charge controllers: step xiii of Fig.~\ref{fig:flow}\\
	\STATE Enforce electrical compatibilities in step xiv of Fig.~\ref{fig:flow} with statement \textbf{assume} and define the inverter \\
	\STATE non-deterministic variables hold feasible equipment and cost \\
	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
 \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

\textcolor{blue}{Next, we use a set of equations to calculate the sizing variables (lines $6$, $7$, $8$, $10$, $11$, $13$, $15$). The statements \textit{assume} (lines $9$, $12$, $14$, and $16$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines. Line $12$ is for the battery bank. Lines $9$ and $14$ are the charge controller voltage check. Line $16$ does the inverter check and ensures the power demand and the surge power of the inverter. Therefore, our synthesis algorithm reaches line $17$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $18$). This cost is the equivalent to Eq.~\eqref{eq:LCC}.}

@@

In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.

\textcolor{blue}{Worth to mention that an optimal solution from a tool is not necessarily the same optimal from other tool, mainly when the data base of equipment items (with different costs) are not the same. Therefore the comparison must take this issue into account.}

%---------------------------------------------------------------------------
\subsection{Threats to validity} 
%---------------------------------------------------------------------------
We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate. Second, improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one. 
%------------------------------------
\section{Conclusions} 
%------------------------------------
Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by the commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market. It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. For future work, %we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.
\textcolor{blue}{now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, in order to speed up the time to response. Using binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$.}

### 2020-07-05 Tex/CAV2019/VSTTE_PV_sizing_Trindade_Cordeiro_2020_unmarked.tex
VSTTE rebuttal

\begin{center}
\textbf{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison} \\

VSTTE 2020 - 12th Working Conference on Verified Software: Theories, Tools, and Experiments\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}. Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed. \textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.

@@

\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days. $DOD$ is the depth of discharge or the fraction of discharge. The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$. However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours). \textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}. When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.

@@

\begin{equation}
\label{eq:Cbank}
\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
\end{equation}

@@

\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}

>>>>

\begin{center}
\textbf{\LARGE Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison} \\
\hfill \break
VSTTE 2020 - 12th Working Conference on Verified Software: Theories, Tools, and Experiments\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}. Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed. An empirical factor of $20$\% for losses is considered~\cite{Pinho}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.

@@

\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days. $DOD$ is the depth of discharge or the fraction of discharge. The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$. However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours). Therefore, the definition given here is for a maximum of $DOD$. When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.

@@

\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}
\end{equation}

@@

The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent (heat can reduce output efficiency by 10-25\%), as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.
